\documentclass[12pt]{article}
\usepackage{caption}
\usepackage{float}
\usepackage{graphicx}
\usepackage{fancyhdr}
\pagestyle{fancy}
\pagenumbering{Roman}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\setlength{\headheight}{25pt}
\rhead{\textbf{Lightning Coalition Robotics}}
\cfoot{}
\rfoot{\thepage}
\begin{document}

% Add date (e.g. September 14, 2018) and then your name/all authors.
September 18, 2019 - Sarah Celaya

\section{Our Plan:} % Pretty self explanatory... In this section explain the team's plan.
\begin{itemize}
% After \item, add what you want for the bullet point. (\item adds a new bullet point when you run out.)
	\item Introduce our team and this year’s challenge
\item Get to know new team members and their level of robotics experience
\item Organize our materials
\item Figure out what we need to buy for this year
\item Form committees and find members for them
\end{itemize}

% Now add a paragraph explaining your plan. You should reference the bullet points above.
Our plan for today was to get through introductions. We want our new team members to meet and get to know the older members. We also wanted to re-watch the challenge video and make sure everyone is aware of what our challenge is this year. We also wanted to get to know our new members and see at what level they are with regards to their experience in robotics. We also wanted to organize our materials and make a list of any missing materials we’re going to need this year (and order those materials of course). The last point on our to-do list is to form committees for the various parts that make up our team.

\section{What We Got Done:} % Just like the above, explain what the team got done during practice.
\begin{itemize}
% After \item, add what you want for the bullet point. (\item adds a new bullet point when you run out.)
	\item We did introductions
\item We got to know new members and their robotics experience level
\item We made sure everyone knew this year’s challenge
\item We organized our materials
\item We made a list of what we were missing that we needed for this year
\item We ordered some missing materials
\item We formed committees
\end{itemize}

% Now add a paragraph explaining what you got done and the reasons behind it. You should reference the bullet points above.
Today we got through our introductions. Everyone got to know everyone else. We also learned about our new members experience with robotics. We watched the challenge video and made sure everyone understood what was basically going to happen for the year. We organized our materials and made a list of parts and tools we were still missing. We ordered what we needed. We also formed 4 basic committees: Coding, Building, Outreach, and Visuals.

\section{What We Didn't Get Done:} % Explain what the team didn't get done during practice.
\begin{itemize}
% After \item, add what you want for the bullet point. (\item adds a new bullet point when you run out.)
	\item Find members for all the committees
\end{itemize}

% Now add a paragraph explaining what you didn't get done and the reasons behind it. You should reference the bullet points above.
Since this practice was on Wednesday, we continued after school. Some students had to leave for sports and other reasons, so we didn’t have everyone sign up for what committees they wanted to be in. We ended up making a google doc and sharing it with the group via Discord.

\section{Next Practice:}
\begin{itemize}
% After \item, add what you want for the bullet point. (\item adds a new bullet point when you run out.)
	\item Start brainstorming for our design
\end{itemize}

% Now add a paragraph explaining what the plan for next practice should be. You should reference the bullet points above.
The next practice is... (Saturday, 9/21/2019 ). 
\end{document}
